### 2008-12-18 talk/ecoop2009/tlc.tex
finish benchmark section, only the tables are missing

Obviously, not all the operations are applicable to all objects. For example,
it is not possible to \lstinline{ADD} an integer and an object, or reading an
attribute from an object which does not provide it.  Being dynamically typed,
the VM needs to do all these checks at runtime; in case one of the check
fails, the execution is simply aborted.

@@

Since reading TLC programs at bytecode level is hard, in this paper we will
use an invented Python-like syntax to describe examples, even if we need to
remind that the actual programs are written in the assembler language showed
above. Thus, the example above can be written in the following way:

>>>>

Obviously, not all the operations are applicable to all types. For example,
it is not possible to \lstinline{ADD} an integer and an object, or reading an
attribute from an object which does not provide it.  Being dynamically typed,
the VM needs to do all these checks at runtime; in case one of the check
fails, the execution is simply aborted.

@@

Since reading TLC programs at bytecode level is hard, in this paper we will
use an invented Python-like syntax to describe examples, although we need to
remind that the actual programs are written in the assembler language showed
above. Thus, the example above can be written in the following way:
